---
title: "Drake"
output: html_notebook
---


Carga de librerías

```{r, echo=FALSE}
library(drake)
library(dplyr)
library(ggplot2)
```

Funcións

```{r}
mi_plan<-drake_plan(hist=create_plot())
plan
config(plan)
```

Funcións de traballo

```{r}
create_plot <- function(data) {
  ggplot(data, aes(x = Petal.Width, fill = Species)) +
    geom_histogram()
}
```

load your custom functions,



check any supporting files (optional),
Ficheiros
```{r}
# Get the files with drake_example("main").
file.exists("raw_data.xlsx")

file.exists("report.Rmd")

```


Creación do plan
```{r}

plan <- drake_plan(
 
  data = iris %>%
    mutate(Species = forcats::fct_inorder(Species)),
  hist = create_plot(data),
  fit = lm(Sepal.Width ~ Petal.Width + Species, data)#,
  # report = rmarkdown::render(
  #   knitr_in("Fluxo.Rmd"),
  #   output_file = file_out("Fluxo.html"),
  #   quiet = TRUE
  #)
)
plan
```


Lanzamento do plan

```{r}
make(plan)
```



Except for files like report.html, your output is stored in a hidden .drake/ folder. Reading it back is easy.
```{r}
readd(data) # See also loadd().
readd(hist)
```


#> # A tibble: 150 x 5
#>    Sepal.Length Sepal.Width Petal.Length Petal.Width Species
#>           <dbl>       <dbl>        <dbl>       <dbl> <fct>  
#>  1          5.1         3.5          1.4         0.2 setosa 
#>  2          4.9         3            1.4         0.2 setosa 
#>  3          4.7         3.2          1.3         0.2 setosa 
#>  4          4.6         3.1          1.5         0.2 setosa 
#>  5          5           3.6          1.4         0.2 setosa 
#>  6          5.4         3.9          1.7         0.4 setosa 
#>  7          4.6         3.4          1.4         0.3 setosa 
#>  8          5           3.4          1.5         0.2 setosa 
#>  9          4.4         2.9          1.4         0.2 setosa 
#> 10          4.9         3.1          1.5         0.1 setosa 
#> # … with 140 more rows



You may look back on your work and see room for improvement, but it's all good! The whole point of drake is to help you go back and change things quickly and painlessly. For example, we forgot to give our histogram a bin width.


#> `stat_bin()` using `bins = 30`. Pick better value with `binwidth`.

So let's fix the plotting function.

Modificación da función

```{r}
create_plot <- function(data) {
  ggplot(data, aes(x = Petal.Width, fill = Species)) +
    geom_histogram(binwidth = 0.25) +
    theme_gray(20)
}
```


```{r}
config <- drake_config(plan)
vis_drake_graph(config) # Interactive graph: zoom, drag, etc.
```

